Review of Assigned Readings

### 2018-01-04 paper/paper.tex
solved ref issues with malkiel1970efficient

%************************** Chapters 1 - Introduction **************************
\begin{spacing}{1.2}
\cleardoublepage\pagenumbering{arabic}
\section{Introduction}
\label{sec:intro}
\textcite[p.~388]{malkiel1970efficient} introduced the Efficient Market Hypothesis (EMH), where they claim that under certain market conditions actual prices include all information. This hypothesis is broadly accepted in the financial world. The digitalisation leads to an increased network effect, where information can be shared over the globe. Based on \citeauthor{mao2015quantifying} (\citeyear[][p.~3]{mao2015quantifying}, as cited in \cite[][pp.~175--195]{shiller2015irrational}; \cite[][pp.~279]{kahneman2013prospect}) the EMH fails to address the behavioural and emotional role of investors. The large fluctuation of the bitcoin prices in the last year (mostly increasing) and the fact that Twitter has become a very popular social network, where people interact, led to different research in the field of sentimental analysis with the focus on bitcoin and twitter. \textcite[p.~18]{mao2015quantifying}, claim that sentiment analysis using twitter tweets which contain the buzzword bullishness can indeed be used as a sentiment indicator for stock prices. As modern economy becomes more digitized, crypotocurrencies as a financial asset draws more attention, our paper seeks to shed some light on whether the tweets can be used to predict bitcoin prices.

@@

%************************** Chapters 3 - Econometric Modelling and Results **************************
\section{Econometric Modelling and Results}
\label{sec:EconometricModellingandResults}
As stated in the beginning, we want to examine the underlying relationship between twitter activity and bitcoin price fluctuations. From our data collection, we are left with two time series datasets representing two variables. A broadly used statistical method to simultaneously analyze multiple time series is the Vector Autoregression (VAR) approach. In this method the endogenous variables are determined both by their own historical values and by the historical values of the other endogenous variables (\cite[pp.~4--5]{lütkepohl2007new}).\\
To generate the econometric results that follow we used the statistical software STATA.

>>>>

%************************** Chapters 1 - Introduction **************************
\begin{spacing}{1.2}
\cleardoublepage\pagenumbering{arabic}
\section{Introduction}
\label{sec:intro}

\textcite[p.~388]{malkiel1970efficient} introduced the Efficient Market Hypothesis (EMH), where they claim that under certain market conditions actual prices include all information. This hypothesis is broadly accepted in the financial world. The digitalisation leads to an increased network effect, where information can be shared over the globe. Based on \citeauthor{mao2015quantifying} (\citeyear[][p.~3]{mao2015quantifying}, as cited in \cite[][pp.~175--195]{shiller2015irrational}; \cite[][pp.~279]{kahneman2013prospect}) the EMH fails to address the behavioural and emotional role of investors. The large fluctuation of the bitcoin prices in the last year (mostly increasing) and the fact that Twitter has become a very popular social network, where people interact, led to different research in the field of sentimental analysis with the focus on bitcoin and twitter. \textcite[p.~18]{mao2015quantifying}, claim that sentiment analysis using twitter tweets which contain the buzzword bullishness can indeed be used as a sentiment indicator for stock prices. As modern economy becomes more digitized, crypotocurrencies as a financial asset draws more attention, our paper seeks to shed some light on whether the tweets can be used to predict bitcoin prices.

@@

%************************** Chapters 3 - Econometric Modelling and Results **************************
\section{Econometric Modelling and Results}
\label{sec:EconometricModellingandResults}
As stated in the beginning, we want to examine the underlying relationship between twitter activity and bitcoin price fluctuations. From our data collection, we are left with two time series datasets representing two variables. A broadly used statistical method to simultaneously analyze multiple time series is the Vector Autoregression (VAR) approach. In this method the endogenous variables are determined both by their own historical values and by the historical values of the other endogenous variables (\cite[pp.~4--5]{luetkepohl2007new}).\\
To generate the econometric results that follow we used the statistical software STATA.
